% moderncv: https://bazaar.launchpad.net/~xdanaux/moderncv/trunk/view/head:/moderncv.cls
% template: https://bazaar.launchpad.net/~xdanaux/moderncv/trunk/view/head:/examples/template.tex
% margins: https://tex.stackexchange.com/a/39030/7918
% vspace: https://tex.stackexchange.com/a/12999/7918
\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.8,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{fontawesome5}
\usepackage{fancyhdr}

\recomputelengths
% hyperref already loaded: https://tex.stackexchange.com/a/79406/7918
\AfterPreamble{\hypersetup{
  pdfencoding=unicode,
}}

\setlength{\hintscolumnwidth}{2.5cm}

\name{Róbert}{\textcolor{color1}{Kohányi}}
\title{Software Engineer}
\address{Miskolc, Hungary}{}{}
\phone[mobile]{+36~20~487~6369}
\email{kohanyi.robert@gmail.com}
\homepage{kohanyirobert.github.io}
\social[github]{kohanyirobert}
\extrainfo{\faStackOverflow\href{https://stackoverflow.com/users/433835/}{ kohanyirobert}}

\newread\versionfile
\openin\versionfile=version.txt
\read\versionfile to\version
\closein\versionfile

\fancyfoot[LE,RO]{
  \textcolor{color2}{Updated at} \textcolor{color3}{\today},
  \textcolor{color2}{version} \textcolor{color3}{\version}
}

\begin{document}
\makecvtitle
\vspace{-2\baselineskip}

\section{Motto}
\cvitem{}{I get the job done.}

\section{Experience}
\cventry{2016--}{Team Lead/Software Developer Mentor}{Codecool Kft.}{Remote/Miskolc}{}{
\begin{itemize}
\item Lead an agile self-organizing team of several technology expert mentors in a remote setting.
\item Oversaw complex resource allocation needs, scheduling, coordinate work between departments.
\item Guided the development and interview preparation successfully for 50+ junior developers.
\item Created engaging introductory SysAdmin/DevOps and Microsoft SQL Server DBA courses.
\end{itemize}}
\cventry{2015--2016}{Software Engineer}{MetaPack Ltd.}{London}{}{
\begin{itemize}
\item Collaborated in the design and drove the implementation of an internal support automation tool.
\item Deployed automated browser-based end-to-end tests using containerization.
\item Improved the efficiency of continuous integration pipelines by introducing fail-fast diagnostics.
\end{itemize}}
\cventry{2013--2015}{Senior Application Developer}{Synergon Integrator Ltd.}{Miskolc}{}{
\begin{itemize}
\item Maintained and improved programmatic communication between various smart metering devices and internal systems.
\item Implemented custom user interface components and complex, long-running background services.
\item Collaborated in a 10+ member, cross-location Scrum team successfully.
\end{itemize}}
\cventry{2009--2013}{Application Developer}{Dolphio Consulting Ltd.}{Miskolc}{}{
\begin{itemize}
\item Created a queryable web-service for a speed trap notifier Android application.
\item Took over operation of and improved a news crawler system in tight client collaboration.
\end{itemize}}

\section{Projects}
\cventry{Video Course}{\href{https://www.packtpub.com/programming/design-patterns-and-solid-principles-with-java-video}{Design Patterns and SOLID Principles with Java}}{Packt Publishing}{}{}{}
\cventry{Cloud/Mobile}{Cloud-based `Music Extractor' with \href{https://github.com/kohanyirobert/aws-lambda-sniff}{AWS Lambda} and \href{https://github.com/kohanyirobert/sniff-android}{Android}}{}{}{}{}
\cventry{Sample Project}{\href{https://github.com/kohanyirobert/spring-boot-backend-sample}{Spring Boot} with \href{https://github.com/kohanyirobert/angular-frontend-sample}{Angular}}{}{}{}{}
\cventry{Automation}{VirtualBox virtual machine image \href{https://github.com/kohanyirobert/vms}{build automation scripts with Python}}{}{}{}{}
\cventry{Interview Test}{\href{https://github.com/kohanyirobert/bluebird-test}{Java Console App using JPA with Hibernate}}{}{}{}{}
\cventry{Master's Thesis}{\href{https://github.com/kohanyirobert/ebson}{Extensible BSON Encoder/Decoder}}{University of Miskolc}{}{}{}

\section{Education}
\cventry{2009--2013}{M.S. Computer Science}{University of Miskolc}{Miskolc}{}{Software Development specialization.}
\cventry{2005--2009}{B.S. Computer Science}{University of Miskolc}{Miskolc}{}{Infocommunication specialization.}

\section{Hard Skills}
\cvitem{Programming}{Expert in Java and C\#, advanced with Python and JavaScript.}
\cvitem{Frameworks}{Experienced with Spring, Java EE, Angular, React .NET Framework/Core.}
\cvitem{Automation}{Intimate with Git, Docker, AWS/Azure, CI/CD and build tools like Maven and Gradle.}

\section{Soft Skills}
\cvitem{Design}{Deep understanding of complex distributed computer systems.}
\cvitem{Analysis}{Exceptional at problem solving and debugging.}
\cvitem{Discipline}{Great time management and goal setting skills.}

\section{Languages}
\cvitemwithcomment{Hungarian}{Native.}{}
\cvitemwithcomment{English}{Fluent.}{}

\end{document}
